Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.

### 2014-10-11 Notes/model.tex
Added writeup about association probability computation and importance sampling.

However, the transmission probability needs to be approximated.  
%
% \subsubsection{Computing $\Prefl$ and $\Ptrans$}
% Focusing on  $\nabla \occfxi$ 
% 
% \begin{multline}
%   \nabla \occfxi =\\
%   \frac{-k\nabla d(\mathbf{x}, \pos{i}{t-1})e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))}}{
%     (1 + e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))})^2
%   } \\ 
%   = -k\nabla d(\mathbf{x}, \pos{i}{t-1})\sech^2\left(\frac{k}{2}(1-d(\mathbf{x},
%   \pos{i}{t-1}))\right)
%   \\
%   = \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
% \end{multline}
% where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
% from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.
% Focusing on $\nabla d(.)$
% 
% \begin{align}
%   \nabla d(\mathbf{x}, \pos{i}{t-1}) = 2\Sigma_i(\mathbf{x} - \pos{i}{t-1})
% \end{align}
% Back to \eqref{eq:analytic-prefl}
% 
% \begin{multline}
%   (\max \{ 0, \nabla \occf^\top \ray \})^2 = \\
%   \sech^4\left(\frac{k}{2}\dishort\right) 
%   (\max \{ 0 , \nabla k\dishort^\top\ray\})^2
% \end{multline}
% 
% The probability is simply $\sech^2(.)$ scaled by gradient of ellipsoid
% $\nabla k\dishort$ projected in the ray direction $\ray$.
% 
% \begin{align}
%   \Ptrans = 
%   e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
% \end{align}
% \begin{multline}
% \int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}
% =  \\
% \int_{1}^{\lambda} \ln{\left(1 - \sum_i \occfi\right)}{d\lambda}
% \end{multline}
% 
% The above integral is very difficult to approximate or compute analytically.
So based on intuition, we approximate the $\Ptrans$ by following function
\begin{align}
\label{eq:evalCumulativePtrans}
  \Ptrans &= \prod_i L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)L_{\lambda}(\lambda; \mu^i_d)\\
  L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u) &= \frac{1}{
    1 + e^{-k_u(1 - (\mathbf{u} - \mu^i_u)^\top\Sigma^i_u(\mathbf{u} -
    \mu^i_u))}
  }
  \\
  L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d) &= \frac{1}{
  1 + e^{-k_d(\lambda - \mu^i_d(\mathbf{u}))}
}
\end{align}
where 
\begin{align}
  \mu_u^i &= \projectionOf{\pos{i}{t-1}} \\
  \Sigma_u^i &= \projectionOf{\Sigma_i}\\
  \mu^i_d(\mathbf{u}) &= \relp{i}{t}\\
  k_u &= 10\log(49)\\
  k_d &= \frac{\log(49)}{\sqrt{h^2 + l^2 + w^2}}
  \label{eq:ptransmissionInit}
\end{align}
is the distance of the centre of the traffic participant from the camera.

@@

\subsection{Numerical integration}
Numerical integration is possible by computed by sampling. Samples need to be
generated from the association probability $\assocP$ for a given $j$. We take
proposal distribution to be a GMM with modes around probable reflection points.
The weights of all Gaussians in the mixture are proportional to the distance of
the point $j$ from projection of ellipsoid centre i.e. $\|\trackpj{t} - \projectionOf{\relp{i}{t}}\|$ . The range of Gaussian $G_i$
must be in the interval $[\|\relp{i}{t}\|, \|\relp{i}{t}\| +
\sqrt{3}\max(\dimsn{i})]$. Hence we take the mean as $\|\relp{i}{t}\| +
\frac{\sqrt{3}}{2}\max(\dimsn{i})$ and variance as
$\frac{1}{3}\max(\dimsn{i})^2$. The distribution from which we sample is 
\newcommand{\Gauss}{\mathcal{N}}
\newcommand{\PropDist}{\mathcal{W}}
\begin{align}
  \PropDist(\lambda) = \sum_i A_i \Gauss(\lambda; \|\relp{i}{t}\| +
  \frac{\sqrt{3}}{2}\max(\dimsn{i}), \frac{1}{\sqrt{3}}\max(\dimsn{i}))
\end{align}
And the numerical integral with $K$ samples is computed by
\begin{align}
    \int_1^{\infty}
    \assocP
    \Ereproj(\lambda)
    d\lambda
    =
    \frac{1}{K}\sum_k \Ereproj \frac{\assocPk}{\PropDist(\lambda_k)}
\end{align}
where $\lambda_k$ is the $k$th sample drawn from $\PropDist(\lambda)$.

>>>>

However, the transmission probability needs to be approximated.  
%
% \subsubsection{Computing $\Prefl$ and $\Ptrans$}
% Focusing on  $\nabla \occfxi$ 
% 
% \begin{multline}
%   \nabla \occfxi =\\
%   \frac{-k\nabla d(\mathbf{x}, \pos{i}{t-1})e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))}}{
%     (1 + e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))})^2
%   } \\ 
%   = -k\nabla d(\mathbf{x}, \pos{i}{t-1})\sech^2\left(\frac{k}{2}(1-d(\mathbf{x},
%   \pos{i}{t-1}))\right)
%   \\
%   = \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
% \end{multline}
% where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
% from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.
% Focusing on $\nabla d(.)$
% 
% \begin{align}
%   \nabla d(\mathbf{x}, \pos{i}{t-1}) = 2\Sigma_i(\mathbf{x} - \pos{i}{t-1})
% \end{align}
% Back to \eqref{eq:analytic-prefl}
% 
% \begin{multline}
%   (\max \{ 0, \nabla \occf^\top \ray \})^2 = \\
%   \sech^4\left(\frac{k}{2}\dishort\right) 
%   (\max \{ 0 , \nabla k\dishort^\top\ray\})^2
% \end{multline}
% 
% The probability is simply $\sech^2(.)$ scaled by gradient of ellipsoid
% $\nabla k\dishort$ projected in the ray direction $\ray$.
% 
% \begin{align}
%   \Ptrans = 
%   e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
% \end{align}
% \begin{multline}
% \int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}
% =  \\
% \int_{1}^{\lambda} \ln{\left(1 - \sum_i \occfi\right)}{d\lambda}
% \end{multline}
% 
% The above integral is very difficult to approximate or compute analytically.
So based on intuition, we approximate the $\Ptrans$ by following function
\begin{align}
\label{eq:evalCumulativePtrans}
  \Ptrans &= \prod_i L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)L_{\lambda}(\lambda; \mu^i_d)\\
  L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u) &= \frac{1}{
    1 + e^{-k_u(1 - (\mathbf{u} - \mu^i_u)^\top\Sigma^i_u(\mathbf{u} -
    \mu^i_u))}
  }
  \\
  L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d) &= \frac{1}{
  1 + e^{-k_d(\lambda - \mu^i_d(\mathbf{u}))}
}
\end{align}
where 
\begin{align}
  \mu_u^i &= \projectionOf{\pos{i}{t-1}} \label{eq:muiudef}\\
  \Sigma_u^i &= \projectionOf{\Sigma_i} \label{eq:sigmauidef}\\
  \mu^i_d(\mathbf{u}) &= \relp{i}{t}\\
  k_u &= 10\log(49)\\
  k_d &= \frac{\log(49)}{\sqrt{h^2 + l^2 + w^2}}
  \label{eq:ptransmissionInit}
\end{align}
is the distance of the centre of the traffic participant from the camera.

@@

\subsection{Numerical integration}
Numerical integration is possible by computed by sampling. Samples need to be
generated from the association probability $\assocP$ for a given $j$. We take
proposal distribution to be a GMM with modes around probable reflection points.
The weights of all Gaussians in the mixture are proportional to the distance of
the point $j$ from projection of ellipsoid centre i.e. 
\begin{align}
  A_{ij} = \frac{1}{Z_j}\exp(-(\trackpj{t} - \mu^i_u)^\top\Sigma_u^i(\trackpj{t} - \mu^i_u))
\end{align}
where $Z_j = \sum_{i=1}^N A_{ij}$ and $\mu^i_u$ and $\Sigma_u^i$ are described in \eqref{eq:muiudef} and \eqref{eq:sigmauidef} respectively.
The range of Gaussian $G_i$
must be in the interval $[\|\relp{i}{t}\|, \|\relp{i}{t}\| -
\sqrt{3}\max(\dimsn{i})]$. Hence we take the mean as $\|\relp{i}{t}\| -
\frac{\sqrt{3}}{2}\max(\dimsn{i})$ and variance as
$\frac{1}{3}\max(\dimsn{i})^2$. The distribution from which we sample is 
\newcommand{\Gauss}{\mathcal{N}}
\newcommand{\PropDist}{\mathcal{W}_j}
\begin{align}
  \PropDist(\lambda) = \sum_i A_{ij} \Gauss(\lambda; \|\relp{i}{t}\| -
  \frac{\sqrt{3}}{2}\max(\dimsn{i}), \frac{1}{\sqrt{3}}\max(\dimsn{i}))
\end{align}
And the numerical integral with $K$ samples is computed by
\begin{align}
    \int_1^{\infty}
    \assocP
    \Ereproj(\lambda)
    d\lambda
    =
    \frac{1}{K}\sum_k \Ereproj \frac{\assocPk}{\PropDist(\lambda_k)}
\end{align}
where $\lambda_k$ is the $k$th sample drawn from $\PropDist(\lambda)$.
